Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-08-13 chapters/chapter01.tex
some comments on the intro

Our group has been involved in research which aims at developing a full quantitative understanding of the processes that shape the epidemiology and the evolution of MEP-like viruses.
In the following section I present the problems on which my involvment in this fascinating area of research has been focused.

@@

Discuss variable size coalescent (demographic) models priors (which are
Introduce phylogeography -- discete ancestral state reconstruction is only one way of doing this (see Bloomquist, Lemey, Suchard)

@@

How this all integrates in a flexible framework and publicly available software

@@

% TODO: white background in plot to be consistent
%---LIKELIHOOD---%
\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{likelihood} 
\caption{
{ \footnotesize 
{\bf  A tree with five taxa.} Character sequence data for single site is observed at the tips of the tree.
} % END: footnotesize
}
\label{fig:LIKELIHOOD}
\end{figure}

>>>>

Our group has been involved in research which aims at developing a full quantitative understanding of the processes that shape the epidemiology and the evolution of MEP-like viruses.
In the following section I present the problems on which my involvement in this fascinating area of research has been focused.

@@

[PL: Discuss variable size coalescent (demographic) models (which are the tree priors in BEAST)
Introduce phylogeography -- discrete ancestral state reconstruction is only one way of doing this (see Bloomquist, Lemey, Suchard)]

@@

[PL: How this all integrates in a flexible framework and publicly available software, one that adequately accounts for phylogenetic uncertainty by averaging over all plausible evolutionary histories for your data
If there is too little here to build a subsection, you can attach it to the previous subsection and call that 'Bayesian genealogical inference using BEAST'
]

@@

%---LIKELIHOOD---%
\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{likelihood} 
\caption{
{ \footnotesize 
{\bf  A tree with five taxa.} Character sequence data for single site is observed at the tips of the tree.
} % END: footnotesize
}
\label{fig:LIKELIHOOD}
\end{figure}
